---
title: ""
output:
  bookdown::pdf_document2:
    toc: false
    includes:
      in_header: preamble.tex
fontsize: 12pt

---
\maketitle

```{r word count, echo = FALSE, eval = FALSE}

# Read the current Rmd file
rmd_file <- "Capstone-49202.Rmd"  

# Read all lines of the Rmd file
lines <- readLines(rmd_file, warn = FALSE)

# Remove YAML header (between first two --- lines)
if (length(lines) > 0 && lines[1] == "---") {
  yaml_end <- which(lines[-1] == "---")[1] + 1
  lines <- lines[-(1:yaml_end)]
}

# Remove code chunks (between ``` and ```)
in_code_chunk <- FALSE
clean_lines <- c()
for (line in lines) {
  if (grepl("^```", line)) {
    in_code_chunk <- !in_code_chunk
    next  # skip the ``` line itself
  }
  if (!in_code_chunk) {
    clean_lines <- c(clean_lines, line)
  }
}

# Remove lines starting with backslash (LaTeX commands like \maketitle)
clean_lines <- clean_lines[!grepl("^\\\\", clean_lines)]

# Collapse to one string for inline removals
text <- paste(clean_lines, collapse = " ")

# Remove inline LaTeX commands like \textbf{...}
text <- gsub("\\\\[a-zA-Z]+\\{[^}]*\\}", "", text)

# Remove inline R code `r ...`
text <- gsub("`r[^`]*`", "", text)

# Remove other inline code with backticks (e.g., `some code`)
text <- gsub("`[^`]*`", "", text)

# Trim whitespace and split into words
words <- unlist(strsplit(text, "\\s+"))
words <- words[words != ""]  # remove empty strings

word_count <- length(words)

cat("Word count excluding YAML, code chunks, inline code, and LaTeX commands:", word_count, "\n")


```

# Abstract
The values and norms define the preferences, behaviors and discourses, and the preferences for promotion and assertion of which vary across contexts and goals. This study aims to analyze the value and norm assertion preferences by the world leaders or senior government officials in their United Nations General Debate (UNGD) speeches, and investigates how they differ from the values and norms of their citizens and the priorities of the United Nations (UN) outlined by the UN Secretary-General’s (UNSG) addresses to the UN General Assembly (UNGA). This research employs natural language processing (NLP) methods to extract the sentences carrying value and norm assertions from the text corpora for the speeches, and uses the data for the seventh wave of World Values Survey (WVS) to acquire the value and norm preferences of world populations. The measurements are aggregated into country level for further analysis, and compared with the population preferences in WVS questions and UNSG addresses. The results demonstrate that there is minimal correlation of value and norm preferences between the leaders or senior government officials and their citizens, in line with the empirical arguments for sui generis value assertions. The findings also suggest the possibility that the values and norms could be composed in speeches in such a way that the value assertions by the leaders do not follow a systematic pattern of preference in the scope of the populations and the UN, indicating context-dependent pragmatic preferences. This research is designed to contribute to the constructivist literature in international relations, by employing a quantitative approach on the value and norm evaluations in diplomatic rhetoric, while addressing the possible limitations and potentials for further research.

# Introduction

The power of language has been leveraged by many actors, including the politicians in their election campaigns with slogans, the leaders or senior government officials in their addresses to international organizations, or companies that mobilize language in their marketing endeavors with striking mottos. The leaders or government representatives in history leveraged the power of language to meet various ends, such as reaffirming the principal values of a nation, as demonstrated in the *Gettysburg Address* by the US President Abraham Lincoln, or forming antithetical relations to out-group values, as in the US President George W. Bush’s use of the word “freedom” versus “tyranny and death” during the “War on Terror” campaign (Sowińska, 2013).

One of the most prominent venues for such words and language to reach to the broader audience is the United Nations General Debate (UNGD), which convenes each year since 1946 under the auspices of the UN General Assembly (UNGA). The UNGD acts as a joint platform for each state's leader to express their positions, views, and perspectives, regardless of their scale, strength, wealth, location, or type of government (Jankin et al., 2024), which was construed as the ‘barometer of international opinion’ (Smith, 2006: 153). This venue has been the scene of diverse referrals to and the promotion of different values and norms in various periods of history, with the example of the rhetorical frictions during Cold War era. As it was accurately pointed out by Finnemore & Sikkink (1998), the early Cold War, “was not simply a positional conflict among anonymous great powers: it was a war for ‘hearts and minds.’’ For instance, while the communist Eastern bloc promoted the collectivist and pro-solidarity discourse into the world plenum, the Western countries advocated for more democracy-embracing and freedom-oriented narrative in their addresses to the General Assembly. 

The selection of value or norm laden language in such addresses is evidently not arbitrary. Rather, they were meticulously chosen by the public diplomacy professionals to best reflect the axiological position of their countries on the ongoing global trends, regional developments, as well as the policies and that should be introduced or amended. The choice of which value to promote, advocate for or disregard depends on the historical, cultural and political outlook of the country, alongside the general outlook of challenges and opportunities that the country, region, or more broadly, multilateral diplomatic system faces. 

Taking this knowledge and perspective into consideration, this study aims to answer the following research questions:

**RQ1**: Do the leaders' preferences of value and norm laden language show an alignment with the value and norm compositions of the nations that they represent? 

**RQ2**: If not, are there systematic patterns in the value assertions of leaders across countries that indicate an alignment with the prevalent value and norm assertion priorities outlined by the UN Secretary-General (UNSG)?

## Values and Norms
The Oxford English dictionary defines values as “the principles or moral standards held by a person or social group; the generally accepted or personally held judgement of what is valuable and important in life.” , while norms are “a standard or pattern of social behavior that is accepted in or expected of a group”. Based on these definitions, values and norms could be perceived as being mutually associated with one another where the norms provide a general outlook on the standard pattern and behavior in a group, and the values are the formed structure of what is accepted, judged or expected.

The relationship between values and norms are implied in various empirical studies, such as cognitive anthropology, sociology, and philosophy. As pointed out by D’Andrade (2017), “values are essentializing concepts, the formulation of a strong causal force within the human psyche”. In this vein, while the norms outline the rules on how a behavior or attitude should take form, the values provide the basis of judgment for what is good or bad (Maltseva, 2018).  Habermas (2003) accurately stressed the hierarchical relationship between the values and norms by noting that, ‘Values- including those which can count on global recognition–are no pie in the sky, but obtain validity exclusively within normative orders and practices of particular cultural lifestyles.’

Although the constructivist international relations literature lacks a single, unified definition of norms, it is nevertheless important to highlight the definitions presented in foundational studies. For instance, norms are defined in the literature as “a standard of appropriate behavior for an actor with a given identity.” (Finnemore & Sikkink, 1998), “standards of behavior defined in terms of rights and obligations.” (Kratochwil & Ruggie, 1986), “shared (thus social) understandings of standards of behavior” (Klotz, 1995). The values, on the other hand, were perceived as principles, foundational norms, or metanorms (Sandholtz, 2007; Wiener, 2008, p. 67; Winston, 2018). Despite lack of consistent definition of values, the propensity for defining values in terms of principles or variants of norms shows coherence with the previously presented framings. Hence, the norms could be perceived as the contributing factor in forming identities and beliefs, and the social norms could be defined as the ‘aspects of social structure that emerged from the actions and beliefs of actors in specific communities’ (Hoffmann, 2017). Thus, values provide the basic power of discernment on what is appropriate or not, and the norms provide the venues of conception for the formation of these values, which jointly contribute to the emergence of value and norm-oriented actions in interpersonal and international settings.

## Norm Diffusion, Norm Cluster and Soft Power 

The notion of norm diffusion, as outlined by Finnemore & Sikkink (1998), posits that the norms are not only static social constructs, but they also proliferate within and across the actors. The concept of norm diffusion can be understood through the theory of norm life cycle, which explains how the norms emerge, attain broader acceptance (i.e., norm cascade), and finally become adopted by other actors (i.e., internalization). In this framework, the norm emergence was initiated by norm entrepreneurs, usually the non-state actors promoting the norms, as the critical agents that promote new norms in an existing upper structures, such as nongovernmental organizations (NGOs) or transnational advocacy networks. Once the norms are being promoted by those entrepreneurs to the point of “critical mass”, the cascade of norms occurs, which equally leads to the advocacy of the emergent norms by the norm leaders. In this phase, the leaders or senior officials could advertise these norms in an existing international setting, such as the United Nations (UN), by means of value and norm-laden diplomatic language.

According Rosenau & Durfee (2000) who introduced the term post-internationalism into the international relations literature, the perspectives of the individual play a central role in the international politics, arguing that the “macro collectivities and institutions derive their sustenance from the individuals they embrace” (Pettersson, 2002). This notion places great emphasis on the actions of the individuals and the collective institutional bodies that they have established. The argument proposed here is significantly resonates with norm life cycle, as the norm entrepreneurs could be perceived as individuals or institutions with a cause that shape the broader entity that they participate, and the leaders’ or senior officials’ contributions to the norm cascade could be evaluated as an endeavor for broader institutional change in accordance with the perspectives of their national, governmental, and international values and norms.

The structure of norms in international relations theory and hierarchical relationship of values with norms was also outlined as the norm cluster by Winston (2018). This study introduces three facets of norms: The problem, the value and and the behavior. In this study, the problem is framed as the issue that requires action, and the values are defined as the driving force behind a given behavior to correct the problem that requires regulation. In addition to the aforementioned definitions of and relationships between norms and values, this nexus provides insights on how these concepts interact in practical sense, specifically when the norms are being propagated within an international organization. 

On the other hand, values and norms are considered as an immutable aspect of the soft power of countries. According to Nye (2011), the soft power of a country primarily hinges on the three critical resources: its culture, political values, and foreign policy. The political values here were described as the polical relationships, structures, perspectives and ideas resulting from the practices of the social forces that ensure the social progress and development (Kallos & Trasnea, 1982). Thus, similar to the beliefs contribute to the foundation of values, the views and ideas contribute to the political values, and thereby contributing to the soft power inventory of the countries.  

## Values and Norms in Political Language

The intersection between norms, culture and political discourse was broadly discussed in social sciences. In this aspect, the norms and culture, with values in tandem, are perceived as ideas and beliefs that are institutionalized that persist over time. One of the main focuses of research in social sciences is on how ideas were institutionalized and norms and culture are constructed. This approach is mostly focused on the embedding of ideas in ‘social norms, patterns of discourse, and collective identities, intangible institutions characterized by intersubjective understandings or shared belief system’, while the ideas being construed as the dynamic aspect of norms (Berman, 2001). As such, the patterns of discourse is one of the key components formed by the political actors that is instrumental in conveying the adopted ideas into broader audience, and the values and norms could constitute a subject of empirical analysis in political discourse.

The power of language in conveying value structures are also highlighted in the discipline of critical linguistics. For instance, Fowler (1996) asserts that all representation formed by the value systems are embedded in the language as a medium, and Fairclough (1989) classifies the values projected onto the systemic aspects of the language into three types – experiental, relational, and textual. In this respect, the texts and textual data, as a form of broader linguistic representation could be perceived as a projection of values and norms of the political actor mobilized with an aim to propagate the values they adopt, to meet a political end or solve a problem in national and international level.

## World Values Survey

The World Values Survey (WVS) is an international research project that focuses on the comparative studies on social, political, religious, and cultural values of populations accross of the world. The survey aims to examine the values, norms and beliefs in cross-cultural and temporal context and evaluate how the trends in values influences the social development. (Haerpfer & Kizilova, 2017). The survey commenced in 1981 and the results of studies are shared with the public in every five years, which are coined as “survey waves”. The recent wave of WVS is the Wave 7, covering the years between 2017 and 2022. Since its inception, the WVS data was used across broad range of topics within the scope of social science and business studies.

The existing literature in computational social sciences predominantly focuses on leveraging value prefererences of countries as measured with WVS to mitigate the biases by Large Language Models (LLMs) (Durmus et al., 2023; Ramezani & Xu, 2023; Zhao et al., 2024).  Other works in this field include measuring online values in on social media posts (Magno&Almeida, 2022), examining prosociality, political attitudes, and Protestant work ethics (Sheetal & Savani, 2021), exploring the value resonances in folktales by classifying texts bases on hypotheses derived from survey responses (Benkler et al., 2022, 2024), discovering key factors on religiosity across countries (Jafarigol et al., 2023), investigating the religio-scientific groups across countries (Lee, 2023), and introducing an exploratory cultural membership classification (Liew et al., 2025). The studies of Benkler et al. will be discussed more broadly in the methodology section.

## United Nations General Debate Speeches and Text Analysis

Extant literature uses text analysis methods to examine UNGD data to address a broad range of social science research questions. This includes the examination of gender representation by international decision-makers (Brun-Mercer, 2021), the rhetorical coherence among the European Union leaders after the Treaty of Lisbon and the attainment of observer status within the UNGA (Hosli & Kantorowicz, 2024), the securitization of climate change in speeches (Arias, 2023), and the topics on international development brought forward by the leaders (Baturo & Dasandi, 2017).

While the main goal was to present their revised UNGD address corpus, the research of Jankin et al. (2024) also employed principal text analysis methods to examine the historical rivalries between the USA and Union of Soviet Socialist Republics/Russia, analyze the engagement of discourses with the Sustainable Development Goals (SDGs), and investigate the reactions of states to Russia’s annexation of Crimea in 2014. Despite being outside of the scope of UNGD speeches, the ongoing research of Grübel et al. (2025) demonstrates that cutting edge quantitative methods were leveraged on the speeches in UN bodies. In addition to text analysis methods, this study employed automated visual emotion recognition to explore the topical and speaker-based variations in the UN Human Rights Council addresses, aiming to study the polarization patterns in discourse.

The work of Shen (2022), on the other hand, is an exemplary study that applies text analysis methods and correlates the findings with cultural metrics from WVS. The study examines overtness of persuasion between the East (East, South, and Southeast Asia) and the West (European Union, North America, and Australia) by employing multidimensional analysis (MDA) methods introduced by Biber (1988). This research incorporates the self-expression dimension of the Cultural Map by Inglehart & Welzel (2005) which is constructed using WVS data, alongside the high- and low-context communication (Morden, 1999), individualism vs. collectivism, and uncertainty avoidance (Hofstede, 2015) patterns in texts.  

Another empirical work by Baturo & Gray (2024) demonstrates that the leaders could find more space to deviate from the UN’s priorities and promote the topics that they deem appropriate for the intergovernmental audience, while focusing the speech on themselves and politicizing the proceedings of UNGD and avoiding the diplomatic language. This study is an indication of the leaders’ potential assertion of the values and norms of their own government, or the population they represent, and the avoidance of diplomatic language provides a potential for clarity in their value and norm assertions. This clarity is also important for text analysis efforts, and the diplomatic language could conceal the value and norm assertions, which could also be perceived as non-preference of assertion by ‘cushioning the blow’ (Bhatia, 2006). The extent to which such *sui generis* value and norm assertions, aligned with leaders’ perspectives, occur consistently across UNGD speeches will be examined in the analysis and discussion section.

The existing research also presented values and norms as the contributing factor for the preparation of speeches by the UN Secretariat members, based on Schwartz's (1992) Basic Human Values (BHV) concept. By conducting interviews with the speechwriting staff of the UN Secretariat in New York from developed and developing countries, the empirical study by Waheed et al. (2013) demonstrated that the UN’s values were the most important contributing factor for the speechwriters, followed by the demographics and the country of origin of the audience, as well as the speechwriters’ values. The results also suggest that values incorporated in speeches that were prepared for the audiences from developed and developing countries show similarities rather than differences. 

In addition, Portman (2014) also employs qualitative text analysis methods based on Schwartz's BHV concept by examining the speeches by the leaders of Finland across two centuries, aiming to shed light on the links between the perspectives of leaders and the populations. By referencing on the Social Identity Theory (Tajfel & Turner, 1979) and arguing that the culture is an “overarching glue” of the national identity and values act as the manifest extension of culture and the leaders’ role in shaping the identity and value structure of the populations. This study demonstrates a unidirectional mechanism of the transfer of values from the populations and to their leaders. 

In summary, the literature on the relationships among the values and norms, leaders, intergovernmental entities propose the following arguments:

-	The leaders’ assertion of values and norms could be shaped by the population that they represent.

-	The populations’ opinions could also be shaped by the leaders, contributing to the identity construction by transforming the societal values and norms.

-	The international organizations’ discourse is mainly shaped by the values and norms of the organization, while also incorporating the values of the audience and speechwriters.

As demonstrated by this review, none of the existing empirical work focuses on the direct usage of WVS to classify the UNGD speech data into the value preference categories to explore the relationships between the values and norms of the populations and speeches of the leaders, as well as presenting quantitative evidence on how the values and norms of the international organizations are reflected on the leaders’ speeches, by directly using the survey questions as indicators for classification. Therefore, this study incorporates the emergent quantitative methods for text analysis and leverages the survey data in WVS to address this empirical gap, while addressing possible limitations. The detailed discussion of the methodological distinction of current study from the existing empirical work will be revisited in the methodology section.

# Data and Methodology

## Data

The primary datasets that are used in this research is the UNGD corpus compiled by Jankin et al. (2024) and the Wave 7 data of WVS gathered by Haerpfer et al. (2022). All data collected is in adherence to the Research Ethics Policy of the London School of Economics and Political Science. The UNGD corpus contains all speeches by the world leaders since the establishment of the UN until the year of 2023, incorporating over 10,000 speeches from 202 countries. The accompanying metadata also provides the details about the identity and the organizational titles of all the speakers, as available. The prior work on the speech corpus by Baturo et al. (2017), highlights that the speeches made in native languages are translated by the UN staff members into the six official languages of the UN (i.e., English, Spanish, French, Russian, Arabic, and Mandarin Chinese), as well as the translation of all non-English speeches into English. Thus, since the resulting dataset contains English texts translated from other languages, concerns about potential semantic and contextual drifts during translation are also valid for this corpus. 

The UNGD speeces could be delivered by heads of state, government or senior government officials, such as the ambassadors or permanent representatives. As noted in the accompanying research article for the corpus, the number of speeches conducted by heads of state or government increased over time, which could present another point of variation due to the leaders of government attaining greater presence to assert value or norm related language, while the holders of bureaucratic posts such as senior diplomats could be bound by the institutional operative guidelines or principles. In the current filtered dataset, 68% of the speeches were delivered by heads of state\footnote{The titles for heads of state in this context are as follows: President, King, Crown Prince (Jordan), Prime Minister, President of The Presidency Council of the Government Of National Accord (Libya), President and Commander-in-Chief of the Defense Forces, Chairman of the Presidential Council.}, while the only ambassador addressing the Assembly is New Zealand’s Permanent Representative to the UN in 2020.

The WVS Wave 7 dataset, on the other hand, contains the survey response data between the years 2017 and 2022, including responses from 62 countries and 4 territories (i.e., Hong Kong, Macau, Northern Ireland, and Puerto Rico). The only country with data collection outside of the scope of the wave is India, of which data was collected in 2023. Based on the rules of WVS, each country is surveyed once per wave. For this reason, the comparisons in this study will be conducted in the context of countries. This research will include the speeches from 61 countries, due to Taiwan not currently being a UN member state. The counts for the number of sentences extracted from the UNGD corpus and the sample sizes for WVS Wave 7 per country are presented in **Table 1**.

The questions that were used for this research are the total of 10 questions. The questions are on the importance of independence, imagination and obedience for children (Q8, Q11, and Q17), trust in armed forces, police, and institutions for justice (Q65, Q69, and Q70) and the preferences for the emphasis on the country’s policies (Q152, Q153, Q154, and Q155). The questions Q153 and Q155 are prepared to measure the secondary set of preferences, as a subsequent for Q152 and Q154, respectively. The full set of questions outlined can be found in the WVS website\footnote{\href{https://www.worldvaluessurvey.org/WVSDocumentationWV7.jsp}{https://www.worldvaluessurvey.org/WVSDocumentationWV7.jsp}}.

The responses to questions Q8, Q11, and Q17 in WVS Wave 7 are binary, with response 1 being “Important” and response 2 is “Not Mentioned”, and for Q65, Q69, Q70 the responses followed an ordinal structure, with response 1 being “A Great Deal” and response  4 “None at all”. The responses to Q152 and Q153 are categorical multiple choice preferences for policy priorities, while the responses are classified among economic growth, strong defence forces, inclusive governance, and the environment. For Q154 and Q155, such priorities are classified as maintaining societal order, inclusive governance, inflation mitigation, and freedom of speech.

After the pre-processing of UNGD samples, selection of valid countries within the survey period, and leaving out too short or too long sentences such that the overall length of sentences would be between 10 and 40 words, the final dataset contained 25, 704 sentences. 

```{r table: combined_table, results='asis', echo=FALSE}

#combined_table.tex

cat("
\\begin{table}[H]
\\caption{UNGD Sentence and WVS Response Sample Sizes}
\\label{tab:combined_split_3wide}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\small
\\renewcommand{\\arraystretch}{1.2}
\\begin{tabularx}{\\textwidth}{lrr @{\\hskip 0.8cm} lrr @{\\hskip 0.8cm} lrr}
\\toprule
\\textbf{Country} & \\textbf{UNGD} & \\textbf{WVS} &
\\textbf{Country} & \\textbf{UNGD} & \\textbf{WVS} &
\\textbf{Country} & \\textbf{UNGD} & \\textbf{WVS} \\\\
\\midrule
AND & 379 & 1004 & IND & 467 & 1692 & NZL & 534 & 1057 \\\\
ARG & 336 & 1003 & IRN & 415 & 1499 & PAK & 733 & 1995 \\\\
ARM & 384 & 1223 & IRQ & 444 & 1200 & PER & 262 & 1400 \\\\
AUS & 484 & 1813 & JOR & 236 & 1203 & PHL & 564 & 1200 \\\\
BGD & 575 & 1200 & JPN & 416 & 1353 & ROU & 274 & 1257 \\\\
BOL & 456 & 2067 & KAZ & 502 & 1276 & RUS & 439 & 1810 \\\\
BRA & 551 & 1762 & KEN & 466 & 1266 & SGP & 485 & 2012 \\\\
CAN & 568 & 4018 & KGZ & 405 & 1200 & SRB & 384 & 1046 \\\\
CHL & 535 & 1000 & KOR & 451 & 1245 & SVK & 298 & 1200 \\\\
CHN & 541 & 3036 & LBN & 316 & 1200 & THA & 372 & 1500 \\\\
COL & 430 & 1520 & LBY & 395 & 1196 & TJK & 342 & 1200 \\\\
CYP & 263 & 1000 & MAR & 305 & 1200 & TUN & 175 & 1208 \\\\
CZE & 394 & 1200 & MDV & 454 & 1039 & TUR & 767 & 2415 \\\\
DEU & 523 & 1528 & MEX & 335 & 1741 & UKR & 551 & 1289 \\\\
ECU & 464 & 1200 & MMR & 357 & 1200 & URY & 313 & 1000 \\\\
EGY & 309 & 1200 & MNG & 361 & 1638 & USA & 768 & 2596 \\\\
ETH & 331 & 1230 & MYS & 574 & 1313 & UZB & 294 & 1250 \\\\
GBR & 439 & 2609 & NGA & 341 & 1237 & VEN & 519 & 1190 \\\\
GRC & 356 & 1200 & NIC & 204 & 1200 & VNM & 325 & 1200 \\\\
GTM & 401 & 1229 & NLD & 458 & 2145 & ZWE & 349 & 1215 \\\\
IDN & 334 & 3200 &       &     &      &      &     &      \\\\

\\bottomrule
\\end{tabularx}
}
\\end{adjustbox}
\\end{table}
")

```

## Methodology

### Methodological Discussion

In the context of UNGD speeches, various methods were leveraged to extract the desired themes or topics in natural language by the researchers, by predominantly applying supervised learning approaches. This includes the identification of the collocates of certain words with the desired set of words using WordSmith Tools 7.0 (Brun-Mercer, 2021; Scott, 2017), using ‘text as data’ methods (Grimmer & Stewart, 2013) to build *a priori* set of dimensions by incorporating wordscores analysis (Hosli & Kantorowicz, 2024), and employing structural topic modelling (STM) on a certain speech segment (i.e., UNGD corpus segment on climate change) to investigate the variations of the given topic with covariates (Arias, 2023). For unsupervised approaches, Watanabe & Baturo (2023) proposed a new approach on the traditional Latent Dirichlet Allocation (LDA) methods by simultaneously introducing seed words and word sequence for semi-supervised topic modelling on UNGD speeches. While the aforementioned study is a robust candidate for text analysis on the corpus which subject to this study as it incorporates sentence-level classification, the resulting topic composition being the sentences composed of a group of words rather than hypothesis sentences prompted an investigation into different models for the analysis.

Furthermore, the research of Grübel et al. (2025) employed the exploration of sentiment of texts in the UN meetings by acquiring the count data of words carrying sentiments and applying multivariate negative binomial distribution with correlated errors with covariates. Although this study allows for simultaneous exploration of the utterances of emotional wording and the variations in facial expressions, the methodological expansion from dictionary based topical assessments and the potential benefits from using embedding based methods to capture subtle semantic nuances in texts were highighted by the researchers. 

In addition to Shen’s (2022) research that examines the linguistic features in UNGD texts and the correlation of the findings with a set of cultural dimensions built on survey data including the WVS responses, various studies have quantitatively explored the values in texts, including the data derived from WVS. For instance, the research of Kiesel et al. (2023) deploys the Touché23-ValueEval dataset (Mirzakhmedova, 2023) derived from the Schwartz’s (1994) value categories to examine the convergence of text data into 20 pre-determined value categories, while one of the teams involved in the study incorporated the WVS based definitional statements, among other survey based data. The teams involved in the study achieved the highest Macro F1 score (0.56) by using the ensemble of 12 transformer based models, specifically (Decoding-enhanced BERT with disentangled attention) DeBERTa and Robustly Optimized BERT-Pretraining Approach (RoBERTa), while the team used survey augmented data achieved a below-chance Macro F1 score (0.46). Although these results do not provide an overwhelming evidence for incorporating survey data regarding values into classification of texts, the methodological scope demonstrates the potential to use such statements as hypotheses for text classification tasks.

The study of Chu et al. (2023), also provides another example of using language models to measure concepts related to opinions to complement the preferences obtained from public surveys. This study leverages a fine-tuned Bidirectional Encoder Representations From Transformers (BERT) model which is trained with data from media diets (i.e., news articles or TV/radio transcripts) using survey questions aimed at measuring the public opinion on Covid-19 pandemic and comparing the results for the trained model with the actual survey responses. Despite the usage of direct survey data for hypothesis building is not a case in this study, the incorporation of direct responses as a comparison benchmark demonstrated a potential for comparative studies between opinion surveys and texts. Also, prompting the model to fill the omitted words for the sentences derived from responses to survey questions is an indicator that the survey questions, or even the responses, could be accurately processed and generated by language models with proper training. 

The group of studies previously mentioned by Benkler et al., (2022, 2024), present an innovative approach by using hypothesis sets derived from WVS responses to classify the sentences or episodic narratives (i.e., a textual premise that communicates an author's perspective on a specific value) by pairing each premise with survey based hypotheses and measuring resonances of values in a given text. These premise and hypothesis pairs were then inserted into a fine-tuned RoBERTa model to provide three possible outcomes: Resonation, confliction and neutrality with a given value hypothesis. Direct appplication of these methods would be out of the scope for the current work, due to the departure from the question-level classification granularity for WVS questionnaire, and broader focus on general value composition in texts. However, the raw expert-annotated WVS hypothesis sentences generated to create World Values Corpus (WVC) in 2024 study were utilized in this research\footnote{Original response hypotheses retained from Benkler et al. (2024); reproduced or adapted under the Creative Commons Attribution 4.0 International License.}, along with a wider set of hypotheses (henceforth they will be mentioned as response and adapted hypotheses, respectively) to bridge the survey and speech domains. Further discussion and the examples of such hypotheses are provided in the next sections.

### Methodological Framework

This study utilizes a Sentence-BERT (SBERT) model *all-mpnet-base-v2* \footnote{Model card available in the following link: \href{https://huggingface.co/sentence-transformers/all-mpnet-base-v2}{https://huggingface.co/sentence-transformers/all-mpnet-base-v2}} in order to acquire the sentence embeddings, and employs a human-in-the-loop iterative sampling procedure in which the model is intermittently included in the sampling loop by acquiring the most uncertain sentences in the sample by using a composite metric and obtanining the subsets within the inter-quartile range (IQR) and maximal marginal relevance (MMR), in order. This metric combines the cosine similarity between a sentence and the label’s prototype (mean) embedding of its adapted hypotheses $C(s,\bar h_c)$; the count of label-specific keywords extracted from response hypotheses $K_c(s)$ (clipped at 2 and normalized as $K_c(s)/2$); binary indicators for KeyBERT n-gram ‘bonus’ phrases from response and adapted hypotheses $(B^{\text{resp}}_c(s),,B^{\text{adap}}_c(s))$; and a label-agnostic rarity score $R(s)$ computed as the min–max–normalized proportion of unique tokens in the sentence that are not among the corpus’s most frequent terms.

$$ \operatorname{Score}_c(s) = 0.6,C(s,\bar h_c) + 0.2,\frac{K_c(s)}{2} + 0.1,B^{\text{resp}}_c(s) + 0.05,B^{\text{adap}}_c(s) + 0.05,R(s) $$
After this procedure, the suggestions were hand-annotated by the author possessing domain knowledge for diplomatic texts. The number of labeled sentences per question and response is outlined in **Table 2**.
```{r table: labeled_data_count, results='asis', echo=FALSE}

cat("
\\begin{table}[H]
\\caption{Number of Hand-Labeled UNGD Sentences per Question and Response}
\\label{tab:labeled_sentence_distribution}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\small
\\renewcommand{\\arraystretch}{1.2}
\\setlength{\\tabcolsep}{7pt}      % inner cell padding
\\begin{tabularx}{\\textwidth}{
  l l r @ {\\hskip 12pt}
  l l r @ {\\hskip 12pt}
  l l r
}
\\toprule
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Count} &
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Count} &
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Count} \\\\
\\midrule
Q8  & 1 & 13 & Q65  & 4 & 47 & Q152, Q153 & 1 & 27 \\\\
Q8  & 2 & 10 & Q69  & 1 & 16 & Q152, Q153 & 2 & 20 \\\\
Q11 & 1 & 21 & Q69  & 2 & 17 & Q152, Q153 & 3 & 23 \\\\
Q11 & 2 & 25 & Q69  & 3 & 12 & Q152, Q153 & 4 & 45 \\\\
Q17 & 1 & 16 & Q69  & 4 & 12 & Q154, Q155 & 1 & 37 \\\\
Q17 & 2 & 10 & Q70  & 1 & 13 & Q154, Q155 & 2 & 42 \\\\
Q65 & 1 & 26 & Q70  & 2 & 28 & Q154, Q155 & 3 & 33 \\\\
Q65 & 2 & 17 & Q70  & 3 & 25 & Q154, Q155 & 4 & 40 \\\\
Q65 & 3 & 41 & Q70  & 4 & 10 &      &   &    \\\\
\\bottomrule
\\end{tabularx}
}
\\end{adjustbox}
\\end{table}
")

```

Followed by the annotation step, 8 models using *CatBoost* as a classifier were trained for questions with binary, ordinal, and multinomial response structure with sentence augmentation, and the testing was conducted with the broader dataset with the most uncertain suggestions, excluding the training set. This procedure was iterated in the cases of misleading signals from training and test procedures. For hyperparameter optimization, *Optuna* package on Python software was used to optimize the F1 evaluation metrics, by introducing Pareto optimum criterion of multi-class responses.

To ensure the full commitment of the model to the diplomatic and political discourse domain, the predicted sentences were filtered in accordance with an additional combined score of model confidence and cosine similarity with the extracted keywords per response. The general formulaic logic for confidence and similarity weighting, thresholding, and the respective definitions for binary and multiclass tasks are as follows:  

Let  
$$
\varphi:\mathcal{S}\to\mathbb{R}^d
$$  
denote the SBERT encoder ($d=768$ for all-mpnet-base-v2), and  
$$
\mathrm{cos}(u,v)=\frac{\langle u,v\rangle}{\|u\|\,\|v\|}
$$  
denote cosine similarity. Sentence–label similarity is defined as  
$$
\mathrm{Sim}(s,c) = \max_{k\in K_c} \mathrm{cos}\big(\varphi(s), \varphi(k)\big),
$$  
where $K_c$ is the set of KeyBERT-extracted N-gram keyphrases for class $c$.  
The joint score is  
$$
J(s) = w_1 \cdot \frac{\mathrm{Conf}_{\%}(s,\hat{c}(s))}{100} + w_2 \cdot \mathrm{Sim}(s,\hat{c}(s)),
$$  
and a sentence $s$ is retained if and only if  
$$
\mathrm{Conf}_{\%}(s,\hat{c}(s)) \ge \tau_1, \quad
\mathrm{Sim}(s,\hat{c}(s)) \ge \tau_2, \quad
J(s) \ge \tau_3,
$$  
where $\tau_1$ is measured in percent, and $\tau_2,\tau_3 \in [0,1]$.

**Confidence definitions**: \newline *Multiclass tasks*: with  
$$
C \ \text{classes}, \quad p_0 = \frac{1}{C}, \quad \hat{c}(s) = \arg\max_{c} p_c(s),
$$  
$$
\mathrm{Conf}_{\%}(s,\hat{c}) = 100 \cdot \max\left\{ 0, \frac{p_{\hat{c}(s)}(s) - p_0}{1 - p_0} \right\}
$$  
(percent above chance level $p_0$). \newline*Binary tasks*: with positive-class probability $p_1(s)$,  
$$
\hat{c}(s) = \mathbf{1}[p_1(s) \ge 0.5],
$$  
$$
\mathrm{Conf}_{\%}(s) = \Delta_{\%}^{\mathrm{chance}}(s) = 100 \cdot \frac{|p_1(s) - 0.5|}{0.5}
$$  
(absolute percent deviation from chance $50\%$).
The hyperparameters used for prediction tasks are presented in **Table 3**. 
```{r table: pred_wvs7_hyperparams_summary, results='asis', echo=FALSE}

#pred_wvs7_hyperparams_summary.tex

cat("
\\begin{table}[H]
\\caption{Prediction Parameters by Model (Full Dataset, $N > 25{,}700$)}
\\label{tab:pred_wvs7_hyperparams_summary}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\Large
\\renewcommand{\\arraystretch}{1.5}
\\begin{tabular}{llcccc}
\\toprule
\\textbf{Model} & \\textbf{Response Type} & \\textbf{Max. Extracted Phrases} & \\textbf{N-Gram Range} & \\textbf{Confidence Criterion} & \\textbf{Conf. Threshold} \\\\
\\midrule
Q8 & Binary & 3 & (5, 7) & \\% Diff. from Chance & 0.01\\% (0.5) \\\\
Q11 & Binary & 1 & (6, 8) & \\% Diff. from Chance & 0.01\\% (0.5) \\\\
Q17 & Binary & 3 & (5, 7) & \\% Diff. from Chance & 0.01\\% (0.5) \\\\
Q65 & Ordinal & 3 & (5, 7) & \\% Above Chance & 2\\% \\\\
Q69 & Ordinal & 3 & (5, 7) & \\% Above Chance & 2\\% \\\\
Q70 & Ordinal & 3 & (5, 7) & \\% Above Chance & 2\\% \\\\
Q152, Q153 & Categorical & 3 & (5, 7) & \\% Above Chance & 2\\% \\\\
Q154, Q155 & Categorical & 3 & (5, 7) & \\% Above Chance & 2\\% \\\\
\\midrule
\\textbf{Model} & \\textbf{Conf. Weight} & \\textbf{Cosine Sim. Weight} & \\textbf{Cosine Sim. Threshold} & \\textbf{Joint Threshold} & \\textbf{Diversity Metric} \\\\
\\midrule
Q8 & 0.50 & 0.50 & 0.40 & 0.01 & 0.30 \\\\
Q11 & 0.50 & 0.50 & 0.40 & 0.01 & 0.30 \\\\
Q17 & 0.50 & 0.50 & 0.40 & 0.01 & 0.30 \\\\
Q65 & 0.30 & 0.70 & 0.45 & 0.30 & 0.30 \\\\
Q69 & 0.30 & 0.70 & 0.45 & 0.30 & 0.30 \\\\
Q70 & 0.30 & 0.70 & 0.45 & 0.30 & 0.30 \\\\
Q152, Q153 & 0.30 & 0.70 & 0.45 & 0.30 & 0.30 \\\\
Q154, Q155 & 0.30 & 0.70 & 0.45 & 0.30 & 0.30 \\\\

\\bottomrule
\\end{tabular}
}
\\end{adjustbox}
\\end{table}
")

```

After the model performances were considered adequate both in terms of the evaluation metrics and the semantic relevance assessed by the author, the models were deployed to classify broader speech corpus. For second-choice questions as Q153 and Q155, the second most frequent predictions were labeled. The results were then recalculated to acquire the proportion of a given response to the set of responses for certain question. Then, the comparison of the actual response proportions by the world populations and the speakers was visualized. In addition, the corpus of the addresses by the UNSG to UNGA within the period of Wave 7 of the WVS were processed and classified for two exemplary questions, to present an analysis of the relative stances of the UNGD speeches per question against the survey respondent’s opinions and the UNSG’s priorities. The specific tools employed in this process are described in detail in the upcoming sections, following the discussion of hypotheses sentences derived from survey responses.

#### Response and Adapted Hypotheses

In addition to the response hypotheses mentioned in the methodological discussion, a set of five adapted hypotheses were generated for each response using assistance from the GPT-4o LLM (OpenAI), followed by human editing to bridge the survey and discourse domains. The initial exploration on the cosine similarity results of these adapted hypotheses with the response hypotheses were above 0.5 excluding the questions Q8, Q11, and Q17, for which questions domain specific contextual augmentations had to be applied. **Table 4** presents a small sample of response and adapted hypotheses employed in this research, while the tools used for the modeling framework and detailed information on the hyperparameters were provided in the **Appendix**.

```{r table: hypotheses, results='asis', echo=FALSE}
#hypotheses.tex

cat("
\\setlength\\LTleft{0pt}   % No left margin
\\setlength\\LTright{0.5pt}  % No right margin

\\renewcommand{\\arraystretch}{0.4} % Compact rows

\\begin{longtable}{p{0.07\\textwidth} p{0.07\\textwidth} p{0.20\\textwidth} p{0.20\\textwidth} p{0.20\\textwidth} p{0.20\\textwidth}}
\\caption{Response and Adapted Hypotheses Examples by Question and Response} \\label{tab:hypotheses} \\\\
\\toprule
\\textbf{Quest.} & \\textbf{Resp.} & \\textbf{Response Hyp.} & \\textbf{Adapted Hyp. I} & \\textbf{Adapted Hyp. II} & \\textbf{Adapted Hyp. III} \\\\
\\midrule
\\endfirsthead

\\caption[]{Response and Adapted Hypotheses Examples by Question and Response (cont.)} \\\\
\\toprule
\\textbf{Quest.} & \\textbf{Resp.} & \\textbf{Response Hyp.} & \\textbf{Adapted Hyp. I} & \\textbf{Adapted Hyp. II} & \\textbf{Adapted Hyp. III} \\\\
\\midrule
\\endhead

\\bottomrule
\\endfoot

Q8 & 1 & It is important for children to be independent. & We believe that nurturing the capacity to act autonomously is central to human dignity. & In our view, societies flourish when individuals are trusted to make decisions for themselves. & Empowering each person to think, choose, and act independently remains a cornerstone of our values. \\\\
\\midrule
Q8 & 2 & It is not important for children to be independent. & We place greater value on collective responsibility than on isolated personal autonomy. & In our society, interdependence and mutual care take precedence over individual separation. & A strong moral compass is shaped not in solitary assertion, but through shared obligations. \\\\
\\\\
\\midrule
Q11 & 1 & It is important for children to be imaginative. & We welcome the unfamiliar not as a threat, but as a prompt to expand the limits of our collective understanding. & It is often in the absence of fixed answers that the deepest forms of insight begin to take shape. & Our growth as a society depends on those moments when curiosity is permitted to exceed instruction. \\\\
\\\\
\\midrule
Q11 & 2 & It is not important for children to be imaginative. & In our experience, the most reliable outcomes arise from the mastery of what already endures. & We find that consistency secures the trust that communities depend upon. & Order does not emerge from flights of speculation, but from careful repetition and restraint. \\\\
\\\\
\\midrule
Q17 & 1 & It is important for children to be obedient. & A well-ordered society begins with those who understand when to listen and when to yield. & The strength of institutions lies in the ability of individuals to respect boundaries not drawn by themselves. & There is merit in restraint, especially when it reflects shared purpose over personal impulse. \\\\
\\\\
\\midrule
Q17 & 2 & It is not important for children to be obedient. & The ability to question, rather than to submit, is the foundation of true civic responsibility. & Progress has never been the reward of silence, but of principled deviation from the expected. & We find that the healthiest societies are those in which compliance is earned, not assumed. \\\\

\\end{longtable}
")




```

Notably, the question based models in this study are not suitable for deployment for different textual datasets and survey questions, and the main intention is to produce a robust pipeline to extract implicit value and norm-laden language per survey question, which could not be extracted with classical unsupervised or semi-supervised approaches such as Generalized Topic Model by Gauthier et al. (2024) and clustering sentence embeddings in *UMAP* and *HDBSCAN* space (Borelli, 2021), or other supervised methods, such as appointing response and adapted hypotheses as centroids to cluster the sentence embeddings (Basu et al., 2002) with embedding cosine similarity as criterion, exploring the possibility of fine-tuning an SBERT model or BERT based classifier, or training neural network models with self-attention for inputs and cross-attention layers across response based hypotheses, with or without ordinal loss metrics such as CORAL or metrics addressing the class imbalance. The main reasons for these methods not providing feasible results could be the requirement for large labeled datasets, implicit assertion of values and norms in UNGD speeches, and the sparsity of such language in discourse, which could be qualitatively corroborated by the examination of the speech documents.

# Analysis and Discussion of Results

This section presents the results of the model performances with discussions on potential strengths and weaknesses, a brief sample of predicted value/norm laden sentences, evaluations on the comparisons of the response level predictions with the actual survey responses, followed by an exemplary tripartite comparisons by incorporating the addresses by the UNSG, and concludes with the linkages of the findings with the existing empirical framework.

## Model Performances

Before presenting the detailed outputs for each question, it would be beneficial to shed light on the differences in response structure and domain adaptation requirements which may have potentially affected model performance. The models produced satisfactory results for the questions that bear multinomial responses, such as Q152 and Q154, possibly due to minimal domain shifting requirement for hypothesis sentences stemming from the direct references to policy priorities. However, the previously mentioned low performance for other approaches called for an adherence to proximate variations of categorical classification tasks for the current model. 

To compensate for the shortcomings on ordinality and domain shifting, iterative domain adaptation efforts and fine-grained labeled data were required during hypothesis building so as to enable the acquisition of robust signals from the corpus. For instance, for the question on the importance of children’s imagination (Q11), general positive attitude towards imaginative behavior, as well as future oriented, imaginative framings such as opening new frontiers, broadening horizons, upholding curiosity, promotion of scientific approach, overt metaphorical language, and deep questioning of values or norms were considered. In addition, for trust in armed forces (Q65), which has an ordinal response structure from “Quite a Lot” to “Not at All”, the adapted hypothesis sentences were constructed such that higher trust level in armed forces would be represented in the first two responses, while the following responses exerting more emphasis on the importance of international peacekeeping operations and total distancing from the favoritism towards the armed forces. The Macro F1 results for question-based models in **Figure 1** visually demonstrate a performance gap despite these efforts, highlighting the relative ease of categorical classifications compared to ordinal or tasks that require heavy domain adaptation.

```{r macro_f1_scores_per_question, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{macro_f1_scores_per_question.png}\n",
  "  \\caption{Macro F1 Scores Across Models}\n",
  "  \\label{fig:macro_f1_scores_per_question.png}\n",
  "\\end{figure}\n"
)

```

Per response F1 scores in the **Table 5** confirm that the model performances are less optimal for the questions outside of the distinct categorical responses. In addition, for binary models of Q8, Q11, and Q17, the permutation tests yielded non-trivial F1 metric scores above 0.5, while retaining a favorable gap with the validation F1 scores per class within the range 0.75 and 0.89. Notably, the permutation F1 scores for such questions showed a slight downward trend as the number of iterations were increased from 20 to 100. This issue is probably due to positive class indicating the existence of a certain value assertion, while the negative class pointing to all other instances without any fine-grained anchoring, as in the case of multi-class tasks. The solution to such suboptimal results could be achieved by introducing additional subclasses in light of the previously mentioned domain adaptation exercise for Q11 to clearly indicate the existence of certain value assertions and adapting the task into multinomial classification in the future research.

Conversely, the ordinal response questions of Q65, Q69, and Q70 provided more reliable results for per-class metrics, with robust permutation test results. The response levels that provide lower F1 scores could be construed as an indicator for the incorporation of more dimensions for domain adaptation, with more emphasis on the extreme cases of high and low trust. The results could also demonstrate that previously mentioned latent stratification exercise for Q65 might be the reason for better evaluation metrics. Also, the applications of such adaptations in trust in police forces (Q69) and institutions of justice (Q70) might have provided too broad or too narrow scopes for each domain. This issue could be more prevalent for Q69, for which the trust in the conduct of the UN peacekeeping operations, or, in a broader sense, UN's role in peace and security were also considered. 

```{r table: f1_score_tables, results='asis', echo=FALSE}

#f1_score_tables.tex

cat("
\\begin{table}[H]
\\caption{F1 Scores for Validation and Permutation Tests by Question and Response}
\\label{tab:f1_scores_table}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\Large
\\renewcommand{\\arraystretch}{1.2}
\\begin{tabular}{llcccc}
\\toprule
\\textbf{Question} & \\textbf{Response} & \\textbf{Validation Set F1} & \\textbf{Permutation Test F1 (Original Training Set)} & \\textbf{Permutation Test F1 (Augmented Training Set)} & \\textbf{Number of Permutations} \\\\
\\midrule
Q8 & 1 & 0.83 & 0.61 & 0.65 & 100 \\\\
Q8 & 2 & 0.75 & 0.33 & 0.34 & 100 \\\\
Q11 & 1 & 0.80 & 0.31 & 0.25 & 100 \\\\
Q11 & 2 & 0.89 & 0.62 & 0.68 & 100 \\\\
Q17 & 1 & 0.89 & 0.74 & 0.76 & 100 \\\\
Q17 & 2 & 0.75 & 0.20 & 0.01 & 100 \\\\
Q65 & 1 & 0.75 & 0.20 & 0.20 & 20 \\\\
Q65 & 2 & 0.60 & 0.14 & 0.16 & 20 \\\\
Q65 & 3 & 0.58 & 0.30 & 0.29 & 20 \\\\
Q65 & 4 & 0.64 & 0.36 & 0.38 & 20 \\\\
Q69 & 1 & 0.50 & 0.22 & 0.32 & 20 \\\\
Q69 & 2 & 0.53 & 0.29 & 0.33 & 20 \\\\
Q69 & 3 & 0.50 & 0.21 & 0.08 & 20 \\\\
Q69 & 4 & 0.67 & 0.19 & 0.21 & 20 \\\\
Q70 & 1 & 0.50 & 0.05 & 0.10 & 20 \\\\
Q70 & 2 & 0.70 & 0.41 & 0.42 & 20 \\\\
Q70 & 3 & 0.57 & 0.39 & 0.39 & 20 \\\\
Q70 & 4 & 0.50 & 0.07 & 0 & 20 \\\\
Q152, Q153 & 1 & 1.00 & 0.20 & 0.19 & 20 \\\\
Q152, Q153 & 2 & 0.82 & 0.26 & 0.11 & 20 \\\\
Q152, Q153 & 3 & 0.88 & 0.26 & 0.12 & 20 \\\\
Q152, Q153 & 4 & 0.91 & 0.40 & 0.47 & 20 \\\\
Q154, Q155 & 1 & 0.87 & 0.22 & 0.20 & 20 \\\\
Q154, Q155 & 2 & 0.91 & 0.23 & 0.33 & 20 \\\\
Q154, Q155 & 3 & 0.87 & 0.19 & 0.21 & 20 \\\\
Q154, Q155 & 4 & 0.88 & 0.31 & 0.28 & 20 \\\\
\\bottomrule
\\end{tabular}
}
\\end{adjustbox}
\\end{table}
    
    ")

```

## Predicted Sentences

One of the key aims of this study was to acquire larger, high-quality samples of value-laden sentences in discourses in comparison to the labeled training data. **Table 6** demonstrates the number of predicted sentences. 

```{r table: pred_data_count, results='asis', echo=FALSE}

cat("
\\begin{table}[H]
\\caption{Number of Predicted UNGD Sentences per Question and Response}
\\label{tab:pred_sentence_distribution}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\small
\\renewcommand{\\arraystretch}{1.2}
\\setlength{\\tabcolsep}{7pt}
\\begin{tabularx}{\\textwidth}{
  l l r @{\\hskip 12pt}
  l l r @{\\hskip 12pt}
  l l r
}
\\toprule
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Count} &
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Count} &
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Count} \\\\
\\midrule
Q8  & 1 & 68   & Q65  & 4 &  31  & Q152, Q153 & 1 &  518 \\\\
Q8  & 2 & 96   & Q69  & 1 &  76  & Q152, Q153 & 2 &  863 \\\\
Q11 & 1 & 32   & Q69  & 2 & 111  & Q152, Q153 & 3 &  435 \\\\
Q11 & 2 & 190  & Q69  & 3 &  65  & Q152, Q153 & 4 &  282 \\\\
Q17 & 1 & 150  & Q69  & 4 & 534  & Q154, Q155 & 1 & 1256 \\\\
Q17 & 2 & 106  & Q70  & 1 & 220  & Q154, Q155 & 2 &  880 \\\\
Q65 & 1 & 165  & Q70  & 2 & 851  & Q154, Q155 & 3 &  188 \\\\
Q65 & 2 &  24  & Q70  & 3 & 159  & Q154, Q155 & 4 &  421 \\\\
Q65 & 3 & 225  & Q70  & 4 &  72  &       &   &      \\\\
\\bottomrule
\\end{tabularx}
}
\\end{adjustbox}
\\end{table}
")

```
As is evident from the counts, the distributions are highly skewed towards certain subsets of the response categories. Potential causes include the inherent limitations from the current sample, requirements for the introduction of additional labeled data in the context of novel linkages between response hypotheses and current speech domain, or the prevalence of moderated value assertions due to the formal and implicit structure of political and diplomatic speeches. It is also beneficial to point out that that the main concern for the predictions being accumulated in null responses (i.e., “not important” or “none”) is alleviated in most of the question-based models, corroborating the claims for signal acquisition. The following table, **Table 7**, provides the qualitative aspects of predictions, followed by discussion  \footnote{Full sample of predicted sentences is provided in GitHub repository.}.




```{r table: sample_sentences, results='asis', echo=FALSE}

#sample_sentences.tex

cat("
\\setlength\\LTleft{0pt}   % No left margin
\\setlength\\LTright{0.5pt}  % No right margin
\\renewcommand{\\arraystretch}{0.6} % Compact rows

\\begin{longtable}{p{0.10\\textwidth} @{\\hskip 4pt} p{0.05\\textwidth} p{0.23\\textwidth} p{0.20\\textwidth} p{0.20\\textwidth} p{0.20\\textwidth}}
\\caption{Response and Adapted Hypotheses Examples by Question and Response} \\\\
\\toprule
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Response Hyp.} & \\textbf{Sentence I} & \\textbf{Sentence II} & \\textbf{Sentence III} \\\\
\\midrule
\\endfirsthead

\\caption[]{Response and Adapted Hypotheses Examples by Question and Response (cont.)} \\\\
\\toprule
\\textbf{Question} & \\textbf{Resp.} & \\textbf{Response Hyp.} & \\textbf{Sentence I} & \\textbf{Sentence II} & \\textbf{Sentence III} \\\\
\\midrule
\\endhead

\\bottomrule
\\endfoot

Q8 & 1 & It is important for children to be independent. & All of this leads us to the conclusion that the Artsakh people's exercise of the right to self determination is of vital importance. & More importantly, we should respect a country's independent choice of development path and model. & Far too many mothers are living in fear, unsure of the fate of their children, and far too many children are seeing their futures crumble in front of them. \\\\
\\midrule
Q8 & 2 & It is not important for children to be independent. & It forced us to acknowledge how interconnected and therefore how reliant we are on one another. & We meet yet again to voice our positions on the major challenges facing our family the human family. & Only when such commitment is guaranteed can we enter a new, brighter chapter in the history of humankind a chapter of cooperation and dialogue a chapter of sustainable peace and development. \\\\
\\midrule
Q152, Q153 & 1 & Over the coming years, the government should emphasize a high level of economic growth. & There is also an urgent need to mobilize resources to help countries in post conflict situations rehabilitate their institutions and begin reconstruction and development. & The path of development that China is pursuing has provided the world with opportunities for shared development. & It will continue to confront difficulties and crises, make breakthroughs and have successes in development. \\\\
\\midrule
Q152, Q153 & 2 & Over the coming years, the government should prioritize ensuring the country has strong defense forces. & On the new frontiers of global governance, such as cyberspace and outer space, state sovereignty must be upheld, rules observed and responsibilities honoured. & Throughout our history, we have worked tirelessly to realize our ambitions both at home and elsewhere in the world. & Globally, we are facing new crises, and many of them, unfortunately, are caused willingly by humans by disrespecting the sovereignty of states. \\\\
\\midrule
Q152, Q153 & 3 & Over the coming years, the government should focus on ensuring that people have more say about how things are done at their jobs and in their communities. & I am talking about this because I am sure that one of the main challenges for humankind today is building democracies that truly speak and listen to the people and achieve the desired results. & We need important reforms among them the reform of the Security Council, whose current configuration reflects a world that no longer exists. & We aim to consolidate our democratic commitment and promote wider citizen engagement in governance. \\\\
\\midrule
Q152, Q153 & 4 & Over the coming years, the government should prioritize work to make the nation's cities and countryside more beautiful. & We provide food security to one sixth of the world's population, even while preserving 66 per cent of our native vegetation and using only 27 per cent of our territory for animal husbandry and agriculture. & We must recommit to achieving sustainable economies, as well as resilient, fair and inclusive societies where no one is left behind. & Another acute problem of our time is related to global climate change. \\\\
\\midrule
Q154, Q155 & 1 & Maintaining order in the nation is of utmost importance. & Mr. President, peace and stability are an indispensable foundation for driving forward the sustainable development agenda, leaving no one behind. & When networks and cartels in government capture the state for their own selfish gain and represent themselves as champions of an ethnic or religious group, the result is all too often civil strife and civil war. & Today's Serbia is committed to peace and, if I may say so, to behaving like an adult. \\\\
\\midrule
Q154, Q155 & 2 & Giving people more say in important government decisions is of utmost importance. & That is to say, on each and every issue that pertains to international coexistence, we have affirmed, and will continue to reaffirm, our commitment to multilateralism and the existence of rules that guarantee the fair treatment of each country. & Egypt, like the vast majority of the world's peoples and nations, has a vested interest in restoring the credibility of international multilateral action with the United Nations at its forefront. & Whether it was taking to the streets or changing our laws, we have seen ourselves as members of a community, one that we have a duty to use our voice within. \\\\
\\midrule
Q154, Q155 & 3 & Fighting rising prices is of utmost importance. & Numerous crises batter our world, crises that are increasingly interlocked regional conflicts with an international impact, devastating climate change, pandemic disruptions, extremist violence, spiralling inflation, looming recession and, for all too many around the world, the growing reality of hunger. & Our planet shared home and mother earth continues to suffer from the serious consequences of consumerism and the excessive greed for natural resources. & At the global level, that demands collective measures to ensure fair access to affordable food and expedite the movement of staples to countries in need. \\\\
\\midrule
Q154, Q155 & 4 & Protecting freedom of speech is of utmost importance. & This must be lauded as there is a dire need to address hate speech domestically. & Moderation is freedom and democracy, conducted in an inclusive and comprehensive manner that does not purport to promote freedom in one place while supporting dictators elsewhere. & In its efforts to promote human rights, the international community must continue to promote respect for fundamental democratic principles throughout the world. \\\\

\\end{longtable}
")


```

The higher performance of questions with multinomial responses (i.e., Q152, Q153, Q154, Q155) also yielded semantically granular predictions, while the response for binary Q8 (i.e., the importance of independence for children) provided weaker alignments even while considering the domain adaptation to incorporate a broader sense of independence, including the emphasis on self-determination or sovereignty. This inconsistency was also prevalent for binary response questions of Q11 and Q17, especially the latter of which yielding prediction samples with signals to opposite class. However, the predictions for the models on ordinal response questions measuring trust in armed forces (Q65), police (Q69), and justice system (Q70) provided more robust alignments, with the weakest qualitative performance in the ‘null’ categories across models -except Q65- typically showing only partial alignment via subtle criticism or calls for reform.

## Proportional Representations of Preferences in UNGD Corpus

The proportion of the preferences in UNDG speeches based on the predictions obtained from one of the models achieving satisfactory results indicate considerable alignments with practical inclinations of countries and geopolitical developments. For instance, as seen in **Figure 2** for the response levels of Q152, China’s growth based international policy discourse, the defence oriented assertions of Iran and USA, and the emergence of such rhetoric by the European countries resulting from the escalations in Eastern Europe is evident from the results. Furthermore, considering the concept of government participation was extended to incorporate the inclusive international governance, the calls from non-P5 countries of UN Security Council for broader participation was accurately captured in addition to the generic emphasis of Global North countries on such norms. In addition, half of the countries for the environment preference being island, tropical, or equatorial countries also points to a robust performance of this particular model. 

```{r q152_top15_props, echo=FALSE, results='asis'}
# Based on Appendix Table A.11, Panel B (longitudinal survey)

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{q152_top15_props.png}\n",
  "  \\caption{Proportions of Response Preferences for Q152 (Top 15 Countries)}\n",
  "  \\label{fig:q152_top15_props.png}\n",
  "\\end{figure}\n"
)

```

\clearpage
When compared with the population surveys on response level, the correlations across countries per response level demonstrated varying results, but consistently yielding weak to no association (Pearson r ranging from -0.20 to 0.35), with distinct gaps in magnitudes of emphasis. The following plot, **Figure 3**, shows an exemplary bipartite comparison of the proportions of classified sentences from UNGD corpus for the first response level of Q152 on the importance of economic growth, yielding essentially no correlation (Pearson r = 0.016) with the proportional, survey-weighted preferences of the populations. This suggests heterogeneous associations across countries, while some countries such as USA, Mongolia, Zimbabwe, and Canada show close alignment of preferences. This figure also demonstrates the over emphasis of Chinese officials on growth, proposing a *sui generis* narrative generation consistent with the geopolitical and geoeconomic aspirations of the administration. Surprisingly, the countries in the Global North showed less preference for such notion in their responses with more significant alignment towards their populations, while sparing more emphasis on pro-defence rhetoric disproportionate to national preferences. The findings on the preferences of defence narrative are provided in the **Appendix**.


```{r q152_1_prop_diffs, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{q152_1_prop_diffs.png}\n",
  "  \\caption{Comparison of Proportional Preferences, UNGD vs. WVS (Q152, 1 – Economic Growth)}\n",
  "  \\label{fig:q152_1_prop_diffs}\n",
  "\\end{figure}\n"
)

```

The following question-level correlation measurements with bootstrapped samples of proportional preferences  in UNGD speeches and WVS responses in **Figure 4** point to insights on both the model performance and associations on a larger scope. For instance, the wider confidence intervals for bootstrapped correlation metrics indicate that either the models for Q8 (independence of children), Q17 (obedience of children), and Q65 (trust in defence forces) were not able to capture consistent signals, or the discourses on such topics show no correlation with the population preferences \footnote{The number of bootstrap iterations was set to 3,000, and the smallest effect size of interest (SESOI) was selected as 0.05. With SESOI set to 0.1, correlations for only Q69, Q70, Q153 and Q154 were identified as robust.}. In contrast, the consistent correlational findings for other questions, albeit weak except Q11 (imagination in children), show that some thematic preferences align with the preferences of the nations. However, the weak negative correlation for Q69 (trust in police) and Q155 (secondary preferences for Q154 on order, inclusive governance, inflation, and freedom of speeches) may suggest direct assertion of these concepts by the leaders or senior officials in contrast with the public opinion, or alignment of value or norm preferences with the UNSG, which will be investigated in the next section. 
```{r corr_bootstrap_sesoi, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{corr_bootstrap_sesoi.png}\n",
  "  \\caption{Question-Level Preference Proportions Between UNGD Speeches and WVS Responses with Bootstrapped Sampling Confidence Intervals (SESOI = 0,05)}\n",
  "  \\label{fig:corr_bootstrap_sesoi}\n",
  "\\end{figure}\n"
)

```

## Leanings of UNGS Predictions versus UNSG Adresses and WVS Responses

To further investigate the relative position of the proportion of value or norm preferences in UNGD speeches, the opening addresses of the UNSG for annual UNGA meetings were incorporated into the investigations on the stances against the populations. In order to ensure full compliance with the data generating process of WVS, the proportional preferences were obtained after summing the counts of the predictions across years \footnote{The year-on-year analysis of the same comparison with the available WVS data also returned similar results pointed out in this section.}. The resulting dataset that contains Jensen-Shannon divergence metrics of three groups of proportion vectors (i.e., UNGD speeches, UNSG addresses, and WVS response) was plotted for visual inference as presented in **Figure 5 and Figure 6** for Q69 and Q155 that previously demonstrated negative correlations. 

To acquire the results for each country $i$, three normalized distributions over the relevant response categories, i.e.,  $p_i$: for UNGD sentences, $w_i$: for WVS responses, and $u$ for UNSG speeches were constructed. Then, similarity was assessed using Jensen–Shannon divergence:  
$$ \mathrm{JSD}(x,y) = \tfrac12 \,\mathrm{KL}(x \parallel m) + \tfrac12 \,\mathrm{KL}(y \parallel m), \quad m = \tfrac12(x+y), $$
where $\mathrm{KL}$ denotes Kullback–Leibler divergence.  Subsequently, the lean index was defined as:  
$$ \mathrm{Lean}_i = \mathrm{JSD}(p_i, u) - \mathrm{JSD}(p_i, w_i), $$
where negative values indicating closer alignment with UNSG priorities,  and positive values with WVS responses.

```{r lean_plot_q69_aggregated_sample20, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{lean_plot_q69_aggregated_sample20.png}\n",
  "  \\caption{Contrastive Comparison of Preference Proportions of UNGD Speeches vs. UNSG Adresses and WVS Responses (Q69, 20 Random Samples)}\n",
  "  \\label{fig:lean_plot_q69_aggregated_sample20}\n",
  "\\end{figure}\n"
)

```

```{r lean_plot_q155_aggregated_sample20, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{lean_plot_q155_aggregated_sample20.png}\n",
  "  \\caption{Contrastive Comparison of Preference Proportions of UNGD Speeches vs. UNSG Adresses and WVS Responses (Q155, 20 Random Samples)}\n",
  "  \\label{fig:lean_plot_q155_aggregated_sample20}\n",
  "\\end{figure}\n"
)

```

The results for all questions suggest that even in questions with positive correlations in **Figure 4**, the predicted UNGD sentences align closer with UNSG addresses, excluding Q153 and Q8 that yield balanced inclinations. The results for Q69 and Q155 also follow the same pattern, without any intensification of alignment towards UNSG priorities. Furthermore, as evident in the figures, some countries are not aligned in either spectrum of preferences, suggesting *sui generis* value and norm assertions by the leaders and senior officials in line with the theoretical framework. Also, the lack of consistencies of countries and patterns across regions indicate that the value and norms are contextually selected by the speakers, with heavier alignments towards UN’s agenda in broader sense.

Possibly, a third axis or a confounder, which could either be internationalist narrative outside of the scope of UNSG’s proposed priorities or a national administrative factor that alters the composition of such proportions for UNGD speeches could be prevalent. An example of the existence of such possible confounder was demonstrated in the *post hoc* exploratory evaluation for Q69 with fewer labeled data, where the country-year proportions for value preferences with country and year fixed effects showed an upward trend across the years. Further diagnostics into this trend by extracting the principal component that positively correlate with year (Pearson r = 0.124) demonstrated an increase in the emphasis on the concepts related to international law by each year, and such trend ceased to appear with the re-labeling with more data. However, this observation could not be replicated into other questions with relatively suboptimal per-class metrics such as Q8, which already yields inconsistent year-on-year observations with provided fixed effects. The confounded and fixed proportions for Q69 were presented with figures in in the **Appendix**, alongside the keyword extraction.

Having presented the technical outlook of the model performances and outputs, the following section discusses the empirical implications of the results within the broader framework, positioning the findings in the context of the previously presented arguments refined from existing literature.

## Connections with the Theoretical Framework

The findings in the study demonstrates that the dominant norm entrepreneur of the largest multilateral diplomacy forum of the world is the most senior executive figure of the forum, as evident with the promoted practical principles and norms. The findings also hint conformities with Waheed et al.’s (2013) study by confirming that the UN’s values and norms are the primary driving force for the preparation of UN officials’ addresses and arguments for such prioritizations may be extended to the motives of the speechwriters from national governments.

In a different vein, the period of this study predominantly coincides with US President Donald Trump’s first term of office, which was marked by the efforts to prioritize bilateral diplomatic ties over the commitments to multilateral international organizations. The values and norms asserted by the most senior official of the UN still resonated with the value and norm discourse of the senior representatives of the world governments. This could highlight the resilience of norm socialization and internalization in the context of values and norms in multilateral diplomacy, even in the face of the attempts to prioritize bilateral foreign policy efforts by one of the world’s leading geopolitical actors.

The previously mentioned arguments on the interplay between the populations, leaders, and international organizations are also reflected in the findings, namely by the example of Chinese administration’s attempts to embed its pro-growth rhetoric into the broader norm structure of the UN, but to a more limited extent. Even still, the effects of such action-takings could be longitudinally studied by measuring the diffusion of given norms across the countries, which could also provide quantitative implications on the “critical mass” concept brought forward in the context of norm life cycle theory.

It is also evident from the findings that the UNGD is not fully perceived as a venue for the confirmation of the position of leaders, and the leaders may not have an absolute discretion over the value and norm assertions, in line with the arguments for “peer pressure” framing of Finnemore & Sikkink (1998) for norm socialization. The decades-long existence of the UN, and the well-established foundational norms of which by the accumulated corpus of agreed languages may have caused a very small subset of countries to bring forward *sui generis* value assertions by considering the underlying risks and benefits for the perceptions on their soft power, particularly in the scope of their administrative prestige and international norm congruence.

It is also important to highlight that with the exceptions of some outliers, the UN-aligned value preference proportions do not demonstrate an overwhelming magnitude. The possibility that this could be due to the “pull” of the national preference proportions while not ruling out the simultaneous back door alignment of UNSG’s and populations’ preferences could still be perceived as relevant. This pattern also maintains the relevance of the value and norm preferences of the populations in leaders’ speeches, albeit with less prominence. Thus, one aspect of the bidirectional relationships as outlined by Portman (2014) that value and norm preferences emanate from the public towards the governments could still be considered relevant, while the dyadic interactions between the populations and the administrations that could result in formal value and norm assertions in the international public diplomacy remain as an avenue for further research.

- *Value (Q8)**: It is important for children to be independent.

- **Problem (UNSG)**: “It is a sad fact of our world today that one's chances of leading a life free of want and in full human dignity still depend more on the circumstances of one's birth than one's innate capacities.” 

- **Behavior 1 (Uzbekistan)**:  “In our country, where over half of the population is young, an extensive work is underway to ensure that every young person takes a worthy place in society and demonstrate their potential.”

- **Behavior 2 (Andorra)**: “We must take advantage of this moment to rebuild and approach this crisis from a gender perspective whereby all women and girls can exercise their freedoms, realize their rights and participate in decision making.”

- **Problem Echo 1 (Argentina)**: “We dream of a world where a child's destiny and a young person's future have no limits other than their talent, intelligence, determination, will power and desire to succeed in life.”

- **Problem Echo 2 (Ecuador)**: “Then comes the stage of inspiring those little ones to enjoy themselves, to play, to study and to be happy.”

Considering this exercise, the current study’s annotation principles can be enhanced by incorporating problem, value, and behavior classifications for the future research that applies to the norm life cycle theory from the perspective of norm clusters with a larger dataset. Future empirical work in this direction could introduce an additional aspect for the previously proposed quantitative measurement efforts to determine the thresholds resulting in cascades of norms.  

# Conclusion

This study examined the extent to which leaders’ preferences for value- and norm-laden language in United Nations General Debate (UNGD) speeches align with the value and norm compositions of the nations they represent, using data from the UNGD corpus compiled by Jankin et al. (2024) and the World Values Survey Wave 7 (Haerpfer et al., 2022) conducted between 2017 and 2022. Employing a sentence-level classification and aggregation pipeline, the analysis positioned the findings within the broader literature on the values and norms in international relations theory, predominantly with Winston’s (2018) norm cluster and Finnemore & Sikkink’s (1998) norm life cycle concepts. In the context of first research question (RQ1), the results demonstrated weak or no cross-country association between the value and norm preferences of leaders or senior government officials and the populations they represent, with varying degrees of gaps in the magnitudes of emphasis. This result indicated that the governments may categorically exert varying levels of emphasis on certain values, while demonstrating inconsistent degrees of departure from the preferences of their nations. To answer the subsequent research question (RQ2), the predictions for the governments and the survey results for the populations were triangulated with the value and norm preferences of the United Nations (UN). To achieve this, the same prediction procedure was applied to the United Nations Secretary-General’s (UNSG) opening remarks for the General Assembly (UNGA). The resulting leaning measurements demonstrated alignments predominantly with UN’s priorities outlined in the addresses of the UNSG, with fewer countries proposing sui generis value statements. All results for the models with robust evaluation metrics and semantic coherence with the survey questions yielded consistent findings with the arguments outlined in the literature in the context of value and norm preference flows within the population-government and international organization-government nexuses. Further exercise on the findings also suggested that the future longitudinal studies of countries with *sui generis* value and norm preferences, with additional data labeling criteria that align with the concept of norm clusters could provide insights into the evolution of the norm life cycle, considering the findings on distinctive patterns for the interpretations of such clusters. 

Practically, the results indicate that similar preemptive measurements on the addresses in multilateral fora could benefit the professionals by creating awareness on the alignments of the proposed speech texts with the value and norm priorities of their nations and the international organizations. In this context, the scope of measurement could also be expanded to investigate the impact of value statements embedded in potentially proposed concepts for joint resolutions or statements. In the cases that such linkages exist, considering such variations in preferences could create another distinctive dimension for like-mindedness, which could result in sustained partnerships even after fulfilling the commitments on common agenda items for task-based country groups.

## Limitations

In addition to the limitations and potential future research directions outlined in the discussion section, the fact that the model pipeline was tailored to the necessities of the current dataset could invoke concerns for generalizability. However, this study does not present an assertion on providing a redeployable model for different datasets, rather it aims to provide an innovative approach to capture implicit textual assertions in the corpus of formal diplomatic speeches by balancing the roles of human annotation and supervised signal extraction. 

On the other hand, direct comparisons between the survey responses and the texts provide various challenges for annotation and measurement tasks. This issue was accurately pointed out in Joseph et al.’s (2021) work regarding the comparison of responses for Covid-19 opinion surveys with the social media posts. In this study the low expert annotation coherence score (Krippendorf’s alpha = 0.4), indicated domain adaptation effots for survey texts is a divisive issue even among the experts in the field. Thus, cross-checking the labeling decisions in this study with a group of experts could optimize the construct validity of human annotation.

# Supplementary Materials


```{r references, results='asis', echo=FALSE}

cat("
# References

- Arias, S. B. (2022). Who securitizes? Climate change discourse in the United Nations. *International Studies Quarterly, 66*(2), Article sqac020. <https://doi.org/10.1093/isq/sqac020>
- Basu, S., Banerjee, A., & Mooney, R. J. (2002). Semi-supervised clustering by seeding. In C. Sammut & A. G. Hoffmann (Eds.), *Proceedings of the Nineteenth International Conference on Machine Learning (ICML ’02)* (pp. 27–34). Morgan Kaufmann Publishers. <https://dl.acm.org/doi/10.5555/645531.656012>
- Baturo, A., & Dasandi, N. (2017). What drives the international development agenda? An NLP analysis of the United Nations General Debate 1970–2016. In *2017 International Conference on the Frontiers and Advances in Data Science (FADS)* (pp. 171–176). IEEE. <https://doi.org/10.1109/FADS.2017.8253221>
- Baturo, A., & Gray, J. (2024). Leaders in the United Nations General Assembly: Revitalization or politicization? *Review of International Organizations, 19*, 721–752. <https://doi.org/10.1007/s11558-023-09524-1>
- Baturo, A., Dasandi, N., & Mikhaylov, S. J. (2017). Understanding state preferences with text as data: Introducing the UN General Debate corpus. *Research & Politics, 4*(2). <https://doi.org/10.1177/2053168017712821>
- Benkler, N., Friedman, S., Schmer-Galunder, S., Mosaphir, D., Sarathy, V., Kantharaju, P., McLure, M. D., & Goldman, R. P. (2022). Cultural value resonance in folktales: A transformer based analysis with the World Value Corpus. In *Social, Cultural, and Behavioral Modeling: 15th International Conference, SBP-BRiMS 2022, Pittsburgh, PA, USA, September 20–23, 2022, Proceedings* (pp. 209–218). Springer-Verlag. <https://doi.org/10.1007/978-3-031-17114-7_20>
- Benkler, N. K., Friedman, S., Schmer-Galunder, S., Mosaphir, D. M., Goldman, R. P., Wheelock, R., Sarathy, V., Kantharaju, P., & McLure, M. D. (2024). Recognizing value resonance with resonance-tuned RoBERTa: Task definition, experimental validation, and robust modeling. In *Proceedings of the 2024 Joint International Conference on Computational Linguistics, Language Resources and Evaluation (LREC-COLING 2024)* (pp. 13688–13698). European Language Resources Association (ELRA) and International Committee on Computational Linguistics (ICCL). <https://aclanthology.org/2024.lrec-main.1195/>
- Berman, S. (2001). Ideas, Norms, and Culture in Political Analysis [Review of *Modernization and Postmodernization...*]. *Comparative Politics, 33*(2), 231–250. <https://doi.org/10.2307/422380>
- Bhatia, A. (2006). Critical discourse analysis of political press conferences. *Discourse & Society, 17*(2), 173–203. <https://doi.org/10.1177/0957926506058057>
- Biber, D. (1988). *Variation across speech and writing*. Cambridge University Press.
- Borrelli, D. (2021, March 16). Clustering sentence embeddings to identify intents in short text. *Towards Data Science*. <https://towardsdatascience.com/clustering-sentence-embeddings-to-identify-intents-in-short-text-48d22d3bf02e>
- Brun-Mercer, N. (2021). Women and men in the United Nations: A corpus analysis of General Debate addresses. *Discourse & Society, 32*(4), 443–462. <https://doi.org/10.1177/0957926521992145>
- Chu, E., Andreas, J., Ansolabehere, S., & Roy, D. (2023). Language models trained on media diets can predict public opinion. *arXiv preprint* arXiv:2303.16779. <https://arxiv.org/abs/2303.16779>
- D’Andrade, R. (2017). From value to Lifeworld. In J. L. Cassaniti & U. Menon (Eds.), *Universalism Without Uniformity: Explorations in Mind and Culture* (pp. 61–74). University of Chicago Press.
- Durmus, E., Nguyen, K., Liao, T. I., Schiefer, N., Askell, A., Bakhtin, A., Chen, C., Hatfield-Dodds, Z., Hernandez, D., Joseph, N., Lovitt, L., McCandlish, S., Sikder, O., Tamkin, A., Thamkul, J., Kaplan, J., Clark, J., & Ganguli, D. (2024). Towards measuring the representation of subjective global opinions in language models. *arXiv preprint* arXiv:2306.16388. <https://arxiv.org/abs/2306.16388>
- Fairclough, N. (1989). *Language and Power*. Longman.
- Finnemore, M., & Sikkink, K. (1998). International Norm Dynamics and Political Change. *International Organization, 52*(4), 887–917. <http://www.jstor.org/stable/2601361>
- Fowler, R. (1996). On critical linguistics. In C. R. Caldas-Coulthard & M. Coulthard (Eds.), *Texts and Practices* (pp. 3–14). Routledge.
- Gauthier, G., Widmer, P., & Ash, E. (2024, November 26). Deep latent variable models for unstructured data (Preliminary version). Retrieved from <https://www.dropbox.com/scl/fi/c30hibel8ad93owfiz2lh/Deep_Latent_Variable_Models_for_Unstructured_Data.pdf?rlkey=xn9u9og0d0a603i4b7j4i511a&st=pisq7110&dl=0>
- Grootendorst, M. (2021). MaartenGr/KeyBERT: BibTeX (v0.1.3). Zenodo. <https://doi.org/10.5281/zenodo.4461265>
- Grübel, J., Hug, S., & Steinert, C. (n.d.). Emotions in international assemblies: Debating human rights in the UN Human Rights Council [Preprint]. Retrieved from <http://christophsteinert.de/current-research/>
- Habermas, J. (2003, April 17). *Frankfurter Allgemeine Zeitung*, p. 23.
- Haerpfer, C., Inglehart, R., Moreno, A., Welzel, C., Kizilova, K., Diez-Medrano, J., Lagos, M., Norris, P., Ponarin, E., & Puranen, B. (Eds.). (2022). *World Values Survey: Round Seven – Country-Pooled Datafile Version 6.0*. JD Systems Institute & WVSA Secretariat. <https://doi.org/10.14281/18241.24>
- Haerpfer, C. W., & Kizilova, K. (2012). The world values survey. In *The Wiley-Blackwell Encyclopedia of Globalization* (pp. 1–5). <https://doi.org/10.1002/9780470670590.wbeog954>
- Hoffmann, M. (2017, December 22). Norms and Social Constructivism in International Relations. *Oxford Research Encyclopedia of International Studies*. Retrieved July 22, 2025, from <https://oxfordre.com/internationalstudies/view/10.1093/acrefore/9780190846626.001.0001/acrefore-9780190846626-e-60>
- Hofstede, G. (2011). Dimensionalizing cultures: The Hofstede model in context. *Online Readings in Psychology and Culture, 2*(1). <https://doi.org/10.9707/2307-0919.1014>
- Hosli, M. O., & Kantorowicz, J. (2024). The European Union in the annual United Nations General Assembly Debates. *Contemporary Politics, 31*(3), 413–438. <https://doi.org/10.1080/13569775.2024.2387424>
- Inglehart, R., & Welzel, C. (2005). *Modernization, cultural change, and democracy: The human development sequence*. Cambridge University Press.
- Jafarigol, E., Keely, W., Hortag, T., & Others. (2023). Religious affiliation in the twenty-first century: A machine learning perspective on the World Value Survey. *Society, 60*, 733–749. <https://doi.org/10.1007/s12115-023-00887-0>
- Jankin, S., Baturo, A., & Dasandi, N. (2024). Words to unite nations: The complete United Nations General Debate Corpus, 1946–present. *Journal of Peace Research, 62*(4), 1339–1351. <https://doi.org/10.1177/00223433241275335>
- Joseph, K., Shugars, S., Gallagher, R., Green, J., Quintana Mathé, A., An, Z., & Lazer, D. (2021). (Mis)alignment Between Stance Expressed in Social Media Data and Public Opinion Surveys. In *Proceedings of EMNLP 2021* (pp. 312–324). Association for Computational Linguistics. <https://aclanthology.org/2021.emnlp-main.27/>
- Kallos, N., & Trasnea, O. (1982). Political Values: Their Status and Social Function. *International Political Science Review, 3*(2), 182–189. <http://www.jstor.org/stable/1600770>
- Kiesel, J., Alshomary, M., Mirzakhmedova, N., Heinrich, M., Handke, N., Wachsmuth, H., & Stein, B. (2023). SemEval-2023 Task 4: ValueEval: Identification of human values behind arguments. In *Proceedings of the 17th International Workshop on Semantic Evaluation (SemEval-2023)* (pp. 2287–2303). Association for Computational Linguistics. <https://aclanthology.org/2023.semeval-1.313/>
- Klotz, A. (1995). *Norms in International Relations: The Struggle against Apartheid*. Cornell University Press.
- Koloski, B., Pollak, S., Škrlj, B., & Martinc, M. (2022). Out of thin air: Is zero-shot cross-lingual keyword detection better than unsupervised? In *Proceedings of LREC 2022* (pp. 400–409). European Language Resources Association. <https://aclanthology.org/2022.lrec-1.42/>
- Kratochwil, F., & Ruggie, J. G. (1986). International organization: a state of the art on an art of the state. *International Organization, 40*(4), 753–775. <https://doi.org/10.1017/S0020818300027363>
- Lee, J. J. (2023). Measuring Cross-National Variations in Religiosity and Attitudes Toward Science and Technology Using Machine Learning. *The Sociological Quarterly, 64*(3), 423–444. <https://doi.org/10.1080/00380253.2023.2165573>
- Liew, K., Hamamura, T., & Uchida, Y. (2025). Machine learning culture: Cultural membership classification as an exploratory approach to cross-cultural psychology. *Personality and Social Psychology Bulletin, 0*(0). <https://doi.org/10.1177/01461672251339313>
- Magno, G., & Almeida, V. (2022). Measuring international online human values with word embeddings. *ACM Transactions on the Web, 16*(2), Article 9. <https://doi.org/10.1145/3501306>
- Maltseva, K. (2018). Values, norms, and social cognition. *NaUKMA Research Papers. Sociology, 1*, 3–9. <https://www.researchgate.net/publication/329978645_Values_norms_and_social_cognition>
- Morden, T. (1999). Models of national culture – A management review. *Cross Cultural Management: An International Journal, 6*(1), 19–44. <https://doi.org/10.1108/13527609910796915>
- Oxford University Press. (n.d.). Norm, n.¹, I.1.b. In *Oxford English Dictionary*. Retrieved July 22, 2025, from <https://doi.org/10.1093/OED/5441844214>
- Oxford University Press. (n.d.). Value, n., II.6.d. In *Oxford English Dictionary*. Retrieved July 22, 2025, from <https://doi.org/10.1093/OED/6638642872>
- Pettersson, T. (2002). Individual Values and Global Governance: A Comparative Analysis of Orientations towards the United Nations. *Comparative Sociology, 1*(3–4), 439–463. <https://doi.org/10.1163/156913302100418538>
- Portman, A. (2014). *From Might to Mandate: Values in rulers' public speeches in Finland 1809–2000*. <https://helda.helsinki.fi/items/88ca9ad4-56e0-455a-bd8b-bdb69d858dd1/full>
- Prokhorenkova, L., Gusev, G., Vorobev, A., Dorogush, A. V., & Gulin, A. (2018). CatBoost: unbiased boosting with categorical features. *Advances in Neural Information Processing Systems, 31*. <https://arxiv.org/abs/1706.09516>
- Ramezani, A., & Xu, Y. (2023). Knowledge of cultural moral norms in large language models. *arXiv preprint* arXiv:2306.01857. <https://arxiv.org/abs/2306.01857>
- Sandholtz, W. (2007). *Prohibiting Plunder: How Norms Change*. Oxford University Press.
- Schwartz, S. H. (1992). Universals in the content and structure of values: Theory and empirical tests in 20 countries. In M. Zanna (Ed.), *Advances in Experimental Social Psychology* (pp. 1–65). Academic Press.
- Scott, M. (2017). *WordSmith Tools* (Version 7). Stroud: Lexical Analysis Software.
- Shen, L. (2022). Culture and explicitness of persuasion: Linguistic evidence from a 51-year corpus-based cross-cultural comparison of the United Nations General Debate speeches across 55 countries (1970–2020). *Cross-Cultural Research, 57*(2–3), 166–192. <https://doi.org/10.1177/10693971221139523>
- Sheetal, A., & Savani, K. (2021). A machine learning model of cultural change: Role of prosociality, political attitudes, and Protestant work ethic. *American Psychologist, 76*(6), 997–1012. <https://doi.org/10.1037/amp0000868>
- Smith, C. B. (2005). *Politics and process at the United Nations: the global dance*. Lynne Rienner Publishers.
- Song, K., Tan, X., Qin, T., Lu, J., & Liu, T.-Y. (2020). MPNet: Masked and permuted pre-training for language understanding. *Advances in Neural Information Processing Systems, 33*, 16857–16867. <https://arxiv.org/abs/2004.09297>
- Sowińska, A. (2013). A critical discourse approach to the analysis of values in political discourse: The example of freedom in President Bush’s State of the Union addresses (2001–2008). *Discourse & Society, 24*(6), 792–809. <https://doi.org/10.1177/0957926513486214>
- Sturua, S., Mohr, I., Akram, M. K., Günther, M., Wang, B., Krimmel, M., ... & Xiao, H. (2024). jina-embeddings-v3: Multilingual embeddings with task LoRA. *arXiv preprint* arXiv:2409.10173. <https://arxiv.org/abs/2409.10173>
- Tajfel, H., & Turner, J. C. (1979). An integrative theory of intergroup conflict. In W. G. Austin & S. Worchel (Eds.), *The Social Psychology of Intergroup Relations* (pp. 33–47). Brooks/Cole.
- Waheed, M., Schuck, A., Neijens, P., & de Vreese, C. (2013). Values in UN speeches: Understanding the speechwriters’ perspectives. *International Communication Gazette, 75*(7), 597–618. <https://doi.org/10.1177/1748048513482542>
- Watanabe, K., & Baturo, A. (2023). Seeded Sequential LDA: A semi-supervised algorithm for topic-specific analysis of sentences. *Social Science Computer Review, 42*(1), 224–248. <https://doi.org/10.1177/08944393231178605>
- Wiener, A. (2008). *The Invisible Constitution of Politics*. Cambridge University Press.
- Winston, C. (2018). Norm structure, diffusion, and evolution: A conceptual approach. *European Journal of International Relations, 24*(3), 638–661. <https://doi.org/10.1177/1354066117720794>
- Zhao, W., Mondal, D., Tandon, N., Dillion, D., Gray, K., & Gu, Y. (2024). Worldvaluesbench: A large-scale benchmark dataset for multi-cultural value awareness of language models. *arXiv preprint* arXiv:2404.16308. <https://arxiv.org/abs/2404.16308>
")

```

# Appendix

## Computational Tools and Modelling Framework 

*All-MPNet-Base-V2*

The SBERT model *all-mpnet-base-v2* leverages the MPNet architecture (Song et al., 2020), a Transformer-based structure produced by Microsoft Research. SBERT models fine-tune Transformer backbones with siamese/triplet setups to produce sentence embeddings where cosine similarity tracks meaning. The MPNet design enhances the performance of traditional models by combining two pretraining techniques: Masked Language Modeling (MLM) and Permuted Language Modeling (PLM). While MLM predicts the randomly masked tokens based on the surrounding context, PLM trains the model to predict the tokens based on varying permutations for the token order, allowing for learning of rich contexts and bidirectional dependencies. In addition, the massive corpus of text used for the training allows for the acquisition of more fine-grained embeddings to capture more subtle and diverse semantic nuances. At this point, it is worth mentioning that due to fine-tuning of these models required a broad labeled dataset for value and norm-laden sentences and given the evident scarcity of signals for this task, the sentence embeddings were instead used for simple classification task with the assistance of a boosting model. 

*CatBoost*

*CatBoost* is a gradient boosting tool developed by Yandex that improves the classical boosting methods employed in other widely used models, such as *XGBoost* or *LightGBM*. This tool yields higher performance in two innovative ways: First, to prevent the information leakage which could potentially occur during greedy boosting or target statistic computation for categorical variables by leveraging an ordered boosting scheme. In this framework, the dataset is randomly permuted, and boosting or target statistics are computed based solely on the preceding samples in the permutation. Second, *CatBoost* natively handles categorical variables without any need for one-hot encoding or external preprocessing, and provides higher performance on these datasets by automatically generating the combinations of categorical features. In addition, *CatBoost* builds symmetrical (oblivious) trees, which helps reduce the risk of overfitting for small data variations by constraining the model complexity into determined boundaries with faster execution at testing time (Prokhorenkova et al., 2018). The developers of *CatBoost* highlighted that the tool supports text embeddings as inputs . 
Although rarely used, boosting models were combined with text embeddings to improve the classification performance in a few studies. For instance, Jovanović et al. (2025) used jina-embeddings-v3 text embedding model (Sturua et al., 2024) to provide automation of the manual invoice posting process in account systems, and Yalçıner et al. (2024) used SBERT embeddings with another boosting model (i.e., LightGBM) to encode Agile project management user stories, resulting in superior accuracy (MAE ≈ 2.15, MdAE = 1.85, SA = 93%) with gains of 12% over baselines and 18% over best alternatives. 

*KeyBERT*

In this study, all keywords are extracted using *KeyBERT* library by Grootendorst (2020) that utilize BERT embeddings for keyword acquisition. In this approach, candidate keyphrases are first sorted according to cosine similarity to the document (i.e., sentence) embedding (coined as Max Sum Distance), and with the optional deployment of MMR based selection they are iteratively selected in accordance with a diversity hyperparameter, with higher diversity generating results with varying cosine similarity scores acquired (Koloski et al., 2022).

*Optuna*

In order to perform hyperparameter optimization separate from the actual model training, *Optuna* library was leveraged to obtain the Pareto optimum F1 scores. This exercise incorporated the optimization procedures for the number of augmented sentences to address the potential labeled data sparsity concerns for the models that provide suboptimal results with default hyperparameters (i.e., models for questions with binary and ordinal responses, excluding the categorical response question models Q152 and Q154) alongside the proportion of the validation set which ranges from 27% to 50%, and early stopping rounds. The other metrics that were optimized using this tool was the learning rate, L2 regularization metric, the amount of randomness used for scoring splits when the tree structure is determined to avoid overfitting (i.e., *random strength*), and Bayesian bootstrap weight randomization parameter (i.e., *bagging temperature*) with higher values indicating more diverse trees. The hyperparameter sets for all models are presented in 

```{r table: training_hyperparams_summary, results='asis', echo=FALSE}

#training_hyperparams_summary.tex

cat("
\\begin{table}[H]
\\caption{Training Hyperparameters by Model}
\\label{tab:training_hyperparams_summary}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\Large
\\renewcommand{\\arraystretch}{1.3}
\\begin{tabular}{llcccccc}
\\toprule
\\textbf{Model} & \\textbf{Response Type} & \\textbf{Sentence Augmentations} & \\textbf{Word Replacements} & \\textbf{Validation Size} & \\textbf{Iterations} & \\textbf{Learning Rate} \\\\
\\midrule

Q8 & Binary & 3 & 1 & 0.40 & 2000 & 0.07 \\\\
Q11 & Binary & 3 & 1 & 0.30 & 2000 & 0.01 \\\\
Q17 & Binary & 7 & 1 & 0.50 & 2000 & 0.01 \\\\
Q65 & Ordinal & 3 & 1 & 0.27 & 2000 & 0.01 \\\\
Q69 & Ordinal & 2 & 1 & 0.45 & 2000 & 0.06 \\\\
Q70 & Ordinal & 5 & 1 & 0.30 & 2000 & 0.03 \\\\
Q152, Q153 & Categorical & 3 & 1 & 0.40 & 2000 & 0.05 \\\\
Q154, Q155 & Categorical & 3 & 1 & 0.40 & 2000 & 0.05 \\\\

\\midrule
\\textbf{Model} & \\textbf{Depth} & \\textbf{L2 Leaf Regularization} & \\textbf{Random Strength} & \\textbf{Bagging Temperature} & \\textbf{Loss Function} & \\textbf{Evaluation Metric} \\\\
\\midrule
Q8 & 5 & 30 & 10 & 10 & Log-Loss & F1 \\\\
Q11 & 5 & 30 & 7 & 15 & Log-Loss & F1 \\\\
Q17 & 4 & 135 & 15 & 0.70 & Log-Loss & F1 \\\\
Q65 & 4 & 32 & 9 & 0.40 & Multi-Class Log-Loss & Macro F1 \\\\
Q69 & 5 & 50 & 2 & 5 & Multi-Class Log-Loss & Macro F1 \\\\
Q70 & 5 & 20 & 7 & 6 & Multi-Class Log-Loss & Macro F1 \\\\
Q152, Q153 & 8 & 10 & 0 & 0 & Multi-Class Log-Loss & Macro F1 \\\\
Q154, Q155 & 8 & 10 & 0 & 0 & Multi-Class Log-Loss & Macro F1 \\\\
\\bottomrule
\\end{tabular}
}
\\end{adjustbox}
\\end{table}
")

```

The following table provides exemplary phrases extracted using *KeyBERT* for the prediction tasks.
```{r table: keyphrase_examples, results='asis', echo=FALSE}

# keyphrase_examples.tex

cat("
\\begin{table}[H]
\\caption{Keyphrase Examples} 
\\label{tab:keyphrases_one_example_count_ordered}
\\centering
\\begin{adjustbox}{width=\\textwidth}
{\\Large
\\renewcommand{\\arraystretch}{1.5}
\\begin{tabular}{llccc}
\\toprule
\\textbf{Question} & \\textbf{Response} & \\textbf{Keyphrase} & \\textbf{Cosine Similarity Score with Grouped Hypotheses} & \\textbf{Keyphrase Count} \\\\
\\midrule
Q8 & 1 & raising children navigate life independence responsibility & 0.807 & 3 \\\\
Q8 & 2 & personal independence harmony social fabric teach children & 0.739 & 3 \\\\
Q11 & 1 & unpredictability necessary aspires evolve encourage children explore unanswered & 0.752 & 1 \\\\
Q11 & 2 & prioritize traditions require reinvention retain value children gain & 0.684 & 1 \\\\
Q17 & 1 & children discipline limitation path collective dignity obedient & 0.820 & 3 \\\\
Q17 & 2 & important children obedient ability question submit & 0.771 & 3 \\\\
Q65 & 1 & national unity resilience reaffirm unwavering trust military & 0.717 & 3 \\\\
Q65 & 2 & nato engagement strengthened capacity affirmed military professionalism & 0.744 & 3 \\\\
Q65 & 3 & peacekeeping operations offered lessons reflections reform csto & 0.760 & 3 \\\\
Q65 & 4 & partisan enforcement military alliances nato csto & 0.704 & 3 \\\\
Q69 & 1 & service reflects rule law finest form peacekeeping & 0.725 & 3 \\\\
Q69 & 2 & trust policing institutions acknowledge continued reforms peacekeeping & 0.816 & 3 \\\\
Q69 & 3 & requiring oversight peacekeeping remains evolving instrument effective & 0.726 & 3 \\\\
Q69 & 4 & accountability misuse power urge reforms international peacekeeping & 0.743 & 3 \\\\
Q70 & 1 & international court justice cornerstone global legal order & 0.787 & 3 \\\\
Q70 & 2 & icc play significant role promoting global justice & 0.770 & 3 \\\\
Q70 & 3 & international legal reflects unequal enforcement universal principles & 0.677 & 3 \\\\
Q70 & 4 & reckoning international rule law mean enforced impartially & 0.657 & 3 \\\\
Q152, Q153 & 1 & economic expansion fundamental pathway national resilience prosperity & 0.753 & 3 \\\\
Q152, Q153 & 2 & prioritize ensuring country strong defense forces affirm & 0.800 & 3 \\\\
Q152, Q153 & 3 & local councils international forums reforming global governance & 0.718 & 3 \\\\
Q152, Q153 & 4 & planet children years come place beauty sustainability & 0.709 & 3 \\\\
Q154, Q155 & 1 & stability public order remain unshaken corner nation & 0.731 & 3 \\\\
Q154, Q155 & 2 & voice global decision making including fairer multilateral & 0.659 & 3 \\\\
Q154, Q155 & 3 & countries suffocated price shocks control rise dignity & 0.746 & 3 \\\\
Q154, Q155 & 4 & protecting freedom speech utmost importance society censors & 0.789 & 3 \\\\
\\bottomrule
\\end{tabular}
}
\\end{adjustbox}
\\end{table}
    
    ")


```


```{r q152_2_prop_diffs, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{q152_2_prop_diffs.png}\n",
  "  \\caption{Comparison of Proportional Preferences, UNGD vs. WVS (Q152, 2 – Strong Defense Forces)}\n",
  "  \\label{fig:q152_2_prop_diffs}\n",
  "\\end{figure}\n"
)

```

```{r counfounded_metrics_q69, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{counfounded_metrics_q69.png}\n",
  "  \\caption{Confounded Metrics for Q69 with Less Labels (Circle Sizes Denote Number of Sentences)}\n",
  "  \\label{fig:counfounded_metrics_q69}\n",
  "\\end{figure}\n"
)

```

```{r confounded_q69_keys, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{confounded_q69_keys.png}\n",
  "  \\caption{Confounding Phrases Extraction}\n",
  "  \\label{fig:confounded_q69_keys}\n",
  "\\end{figure}\n"
)
```

```{r sorted_q69_with_fe, echo=FALSE, results='asis'}

cat(
  "\\begin{figure}[H]\n",
  "  \\centering\n",
  "  \\includegraphics[width=\\textwidth,height=0.24\\textheight]{sorted_q69_with_fe.png}\n",
  "  \\caption{Sorted Q69 Metrics with More Labeled Data}\n",
  "  \\label{fig:sorted_q69_with_fe}\n",
  "\\end{figure}\n"
)
```